The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-11 Writeup/paper_v3.tex
Captions in Table 1 explained

\rachel{DES is far from the only survey; since I'm in HSC and the work was supported by Euclid project, it seems strange to only mention DES.  I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
\arun{Done.}
Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep{HSC_Overview}, Dark Energy Survey~\citep{DESC}, the KIlo-Degree Survey~\citep{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep{PanSTARRS_2010},
the Large Synoptic Survey Telescope~\citep{LSST_Book},Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep{WFIRST_Final}
are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes. Weak lensing happens to be the cleanest probe for this purpose.
As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted. Weak lensing also causes magnification in addition to introducing a shear.
%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.

@@

\rachel{Tables need to be in a table environment, with a caption.  Also, you should include the uncategorized slices in here.} \arun{Done.}
\begin{table} 
\centering
\begin{tabular}{|r|c|c|c|c|}
 \hline
 Redshift & Environment & \s$1$ & \s$2$ & \s$3$ \\
 \hline
 0.3-0.4 & Overdense & 1726 & 2505 & 1260 \\
 0.4-0.475 & Neutral & 988 & 1317 & 710 \\
 0.475-0.55 & Neutral & 1410 & 1788 & 902 \\
 0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\
 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
 0.75-0.8 & Underdense & 1159 & 1196 & 675 \\
 0.8-0.85 & Overdense & 2428 & 2428 & 1630 \\
\end{tabular}
\caption{List of different redshift bins, their environmental classification and the number of galaxies in them for 3 different ways of constructing a volume-limited sample. See text for more details.}
\label{table:GalaxyCounts}
\end{table}

@@

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs. & K-S & 1.1e-4 & 3e-5 & 0.0 \\
  All underdense    & A-D & 1e-5 & 0.0 & 0.0 \\ \hline 
  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.613 & 0.431 & 0.231 \\
  $z:[0.80,0.85]$ (OD) & A-D & 0.494 & 0.237 & 0.130 \\ \hline
  $z:[0.65,0.75]$ (OD) vs & K-S & 5.8e-4 & 2e-5 & 0.0 \\
  $z:[0.55,0.65]$ (UD) & A-D & 9.8e-4 & 0.0 & 0.0 \\ \hline
 \end{tabular}
 \caption{\arun{I can't get the vertical lines in MNRAS:( \\}
 $p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs. \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins. \s$1$, \s$2$, \s$3$ refer to the three ways of generating a volume-limited sample (See \S\ref{sub:volumelimiting}).
          }
 \label{table:pvalues_all}
\end{table}

\begin{figure*}
 \centering
 \includegraphics[width=2.3\columnwidth]{axis_ratio_all_all}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
 \caption{The distributions of axis ratios in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right). The upper panels show the histogram
 and the botom panels show the empirical cumulative distribution function (ECDF). $p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table.~\ref{table:pvalues_all}. The difference between the CDFs turn out to be statistically significant.}
 \label{fig:axisratio_all}
\end{figure*}

@@

When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed. We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}.

For other morphological parameters, we do not the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}. We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure*}
 \centering
 \includegraphics[width=\columnwidth]{median_sersicn}
 \includegraphics[width=\columnwidth]{median_sersicn(2)}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure*}

>>>>

\rachel{DES is far from the only survey; since I'm in HSC and the work was supported by Euclid project, it seems strange to only mention DES.  I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
\arun{Done.}
Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep[HSC;][]{HSC_Overview}, Dark Energy Survey~\citep[DESC;][]{DESC}, the KIlo-Degree Survey~\citep[KIDS;][]{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep[PanSTARRS;][]{PanSTARRS_2010},
the Large Synoptic Survey Telescope~\citep[LSST;][]{LSST_Book}, Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep[WFIRST;][]{WFIRST_Final}
are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes. Weak lensing happens to be the cleanest probe for this purpose.
As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted. Weak lensing also causes magnification in addition to introducing a shear.
%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.

@@

\rachel{Tables need to be in a table environment, with a caption.  Also, you should include the uncategorized slices in here.} \arun{Done.}
\begin{table} 
\centering
\begin{tabular}{|r|c|c|c|c|}
 \hline
 Redshift & Environment & \s$1$ & \s$2$ & \s$3$ \\
 \hline
 0.3-0.4 & Overdense & 1726 & 2505 & 1260 \\
 0.4-0.475 & Neutral & 988 & 1317 & 710 \\
 0.475-0.55 & Neutral & 1410 & 1788 & 902 \\
 0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\
 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
 0.75-0.8 & Underdense & 1159 & 1196 & 675 \\
 0.8-0.85 & Overdense & 2428 & 2428 & 1630 \\
\end{tabular}
\caption{List of different redshift bins, their environmental classification and the number of galaxies binwise for volume-limited samples constructed in three different ways: using hard luminosity cut (\s$1$), letting the luminosity cut evolve with redshift (\s$2$) and imposing stellar-mass cuts (\s$3$).}
\label{table:GalaxyCounts}
\end{table}

@@

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | r | c | c | c | c | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & Tests & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs. & K-S & 1.1e-4 & 3e-5 & 0.0 \\
  All underdense    & A-D & 1e-5 & 0.0 & 0.0 \\ \hline 
  $z:[0.65,0.75]$ (OD) vs. & K-S & 0.613 & 0.431 & 0.231 \\
  $z:[0.80,0.85]$ (OD) & A-D & 0.494 & 0.237 & 0.130 \\ \hline
  $z:[0.65,0.75]$ (OD) vs & K-S & 5.8e-4 & 2e-5 & 0.0 \\
  $z:[0.55,0.65]$ (UD) & A-D & 9.8e-4 & 0.0 & 0.0 \\ \hline
 \end{tabular}
 \caption{$p$-values from the Kolmogorov-Smirnov (K-S) and Anderson-Darling (A-D) obtained by comparing the distributions of axis ratios are given for three cases: \emph{all} overdense (OD) vs. \emph{all} underdense (UD), two overdense bins, not very separated in redshift and a pair of adjacent overdense and underdense bins. \s$1$, \s$2$, \s$3$ refer to the volume-limited sample in three different ways.}
 \label{table:pvalues_all}
\end{table}

\begin{figure*}
 \centering
 \includegraphics[width=2.3\columnwidth]{axis_ratio_all_all}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
 \caption{The distributions of axis ratios of galaxies in \emph{all} overdense (OD) and \emph{all} underdense (UD) regions in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right). The upper panels show the histogram
 and the botom panels show the empirical cumulative distribution function (ECDF). $p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table.~\ref{table:pvalues_all}. The difference between the CDFs turn out to be statistically significant.}
 \label{fig:axisratio_all}
\end{figure*}

@@

When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed. We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}. 
Such a trend is not observed in axis ratios based on second moments. 
For other morphological parameters, we do not the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}. We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure*}
 \centering
 \includegraphics[width=\columnwidth]{median_sersicn}
 \includegraphics[width=\columnwidth]{median_sersicn(2)}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure*}
